Prototype city generation for mobility simulation in urban typologies: a generalized framework

### 2017-12-21 manuscript/manuscript.tex
typology table

>>>>

\begin{table}[h!]
  \centering
  \begin{tabular}{l l l}\toprule
    \bf SN &\bf Name &\bf Supply candidate \\\midrule
    1 & Auto Sprawl & Baltimore \\
    2 & Innovative Heavyweights & Madrid \\
    3 & Sustainable Anchors & Vancouver \\
    4 & Congested Middleweights & Bandung \\
    5 & Boomers & Lagos \\
    6 & Emerging Green Anchors & Hiroshima \\
    7 & Dense Clique & Isfahan\\
    8 & Hybrid Congested & Mashdad \\
    9 & BRT-{\it STAR}s & Sao Paulo  \\
    10 & Metro-Bike Giants & Dalian \\ \bottomrule
  \end{tabular}
  \caption{Prototype city descriptions and candidates}
  \label{tab:proto}
\end{table}
